---
title: "Code"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import Libraries
```{r}
library(haven)
library(broom)
library(magrittr)
library(dplyr)
library(arm)
library(ggplot2)
library(stats)
library(tidyr)
library(fastDummies)
library(vtable)
library(bartCause)
```

# Listing confounders, treatment and outcome
Treatment - 1 where response to I3 is 1 or 2, else 0

Outcome : Support for DEI policy - 6 - Avg of all 8 G question responses 

Confounders - 

1. S1 to S4 (pri 1)
2. I1 I2 (pri 1)
3. PARTY7 - categorical - make dummy (pri 1)
4. REL1 - categorical - make dummy (1-14, 7 missing) (pri 1)
5. REL2 - continuous(1-9) (pri 2) Is this necessary?
6. Demographics -
PPAGE - continuous age varibale (pri 2)
<!-- PPAGECAT - age divided into 7 categories -->
<!-- PPAGECAT4 - age divided into 4 categories -->

Choose one of the above and make dummies for categorical

<!-- PPEDUC - education into 14 categories -->
PPEDUCAT - education into 4 categories (pri 1)

Choose one of the above and make dummies for categorical

PPETHM - race/ethnicity categorical - make dummy (only 1,2, 4 exist in the data) (pri 1) - should be 1 right?
PPGENDER - gender categorical
PPHHHEAD - household head categorical (pri 3)
PPHHSIZE - continuous (pri 3)
PPHOUSE - housing type categorical - make dummy (pri 3)
PPINCIMP - house hold income categorical - make dummy (pri 3)
PPMARIT - Marital status categorical - make dummy (pri 2)
PPMSACAT - msa status categorical - already 0, 1 (pri 2)

PPREG4 - which region of america 4 categories (pri 2)
<!-- ppreg9 - which region of america 9 categories -->

Choose one of the above and make dummies for categorical

PPRENT - ownership status of home categorical - make dummy - highly likely to be correlated with house hold income (pri 3)

Number of household members in that age group - (pri 3)
PPT01
PPT25
PPT612
PPT1317
PPT18OV

PPWORK - current employment status categorical - make dummy (pri 1)
PPNET - internet access presence categorical 1/0 (pri 1)

ESTIMAND - ATT

Approaches - 

Prop score w/ Neaest matching with Replacement
IPTW 
GenMatch
BART


# Load and describe data
```{r}
data0 <- read_sav("./TESS2 118_Bielby_Client.sav")
data1 <- data0 %>% drop_na(E2_1G) #dropping race focus group
# summary(data1)
# hist(data1$S1)
# hist(data1$S2)
# hist(data1$S3)
# hist(data1$S4)
# hist(data1$I1)
# hist(data1$I2)
# hist(data1$PARTY7)
# hist(data1$REL1)
# hist(data1$REL2)
# hist(data1$PPEDUCAT)
# hist(data1$PPETHM)
# hist(data1$PPGENDER)
# hist(data1$PPHOUSE)
# hist(data1$PPINCIMP)
# hist(data1$PPMARIT)
# hist(data1$PPMSACAT)
# hist(data1$PPREG4)
# hist(data1$PPRENT)
# hist(data1$PPWORK)
# hist(data1$PPNET)
```

# Data Preprocessing
```{r}
data2 <- filter(data1, S1 > -1 & S2> -1 & S3 > -1 & S4 > -1 & I1 > -1 & I2 > -1 & REL1 > -1 & REL2 > -1)
data3  <- data2 %>% mutate(treatment_var = ifelse(I3 == 1 | I3 == 2, 1, 0)) %>% mutate(outcome_var = (6 - (E2_1G+E2_2G+E2_3G+E2_4G+E2_5G+E2_6GA+E2_7G+E2_8GA)/8)) # Now outcome variable is support in increasing order of value, i.e outcome_var = 1 is less support and outcome_var = 5 is more support. 
# vtable(data3)
# data4 <- data3 %>% mutate(gender_cat = ifelse(PPGENDER == 1, 1, 0))
data4 <- data3
# data5 <- dummy_cols(data4, select_columns=c('S1', 'S2', 'S3', 'S4', 'I1', 'I2', 'PARTY7', 'REL1', 'REL2', 'PPEDUCAT','PPETHM', 'PPHOUSE', 'PPINCIMP', 'PPMARIT', 'PPREG4', 'PPRENT', 'PPWORK'))
data5 <- data4
outcome_treated <- data5 %>% filter(treatment_var==1)
outcome_control <- data5 %>% filter(treatment_var==0)
hist(data5$treatment_var)
hist(outcome_treated$outcome_var)
hist(outcome_control$outcome_var)
# data5_for_summary <- data4 %>% mutate(factor(treatment_var), factor(S1), factor(S2), factor(S3), factor(S4), factor(I1), factor(I2), factor(PARTY7), factor(REL1), factor(REL2), factor(PPGENDER), factor(PPEDUCAT), factor(PPETHM), factor(PPHOUSE), factor(PPINCIMP), factor(PPMARIT), factor(PPREG4), factor(PPRENT), factor(PPWORK), factor(PPNET), factor(PPMSACAT), factor(PPHHHEAD), cols.break=3) 
# st(data5, vars = c('PPAGE', 'PPHHSIZE', 'outcome_var'), out='latex', summ = c('notNA(x)', 'median(x)', 'mean(x)',   'sd(x)', 'min(x)', 'max(x)'))
# st(data5_for_summary, vars = c('factor(treatment_var)','factor(S1)', 'factor(S2)', 'factor(S3)', 'factor(S4)', 'factor(I1)', 'factor(I2)', 'factor(PARTY7)', 'factor(REL1)', 'factor(REL2)', 'factor(PPGENDER)', 'factor(PPEDUCAT)', 'factor(PPETHM)', 'factor(PPHOUSE)', 'factor(PPINCIMP)', 'factor(PPMARIT)', 'factor(PPREG4)', 'factor(PPRENT)', 'factor(PPWORK)', 'factor(PPNET)', 'factor(PPMSACAT)', 'factor(PPHHHEAD)'), out='latex')
```

```{r}
plot(data5$treatment_var, data5$outcome_var)
```


# Vanilla Linear Regression 
```{r}
vanilla_lin_reg1 <- lm(outcome_var ~ treatment_var, data=data5, model=TRUE, x=TRUE, y=TRUE, qr=TRUE)
summary(vanilla_lin_reg1)
vanilla_lin_reg2 <- lm(outcome_var ~ treatment_var + factor(S1) + factor(S2) + factor(S3) + factor(S3) + factor(S4) + factor(I1) + factor(I2) + factor(PARTY7) + factor(REL1) + factor(REL2) + PPAGE + factor(PPEDUCAT)+ factor(PPETHM) + factor(PPGENDER)  + factor(PPHHHEAD) + PPHHSIZE + factor(PPHOUSE) + factor(PPINCIMP) + factor(PPMARIT) + factor(PPMSACAT) + factor(PPREG4) + factor(PPRENT) + PPT01 + PPT25 + PPT612 + PPT1317 + PPT18OV + factor(PPWORK) + factor(PPNET), data=data5, model=TRUE, x=TRUE, y=TRUE, qr=TRUE)
summary(vanilla_lin_reg2)
```
# BART

```{r}
bart_res <- bartc(outcome_var, treatment_var, factor(S1) + factor(S2) + factor(S3) + factor(S3) + factor(S4) + factor(I1) + factor(I2) + factor(PARTY7) + factor(REL1) + factor(REL2) + PPAGE + factor(PPEDUCAT)+ factor(PPETHM) + factor(PPGENDER)  + factor(PPHHHEAD) + PPHHSIZE + factor(PPHOUSE) + factor(PPINCIMP) + factor(PPMARIT) + factor(PPMSACAT) + factor(PPREG4) + factor(PPRENT) + PPT01 + PPT25 + PPT612 + PPT1317 + PPT18OV + factor(PPWORK) + factor(PPNET), data = data5, method.rsp = "bart", method.trt = "bart", estimand = 'att', crossvalidate = TRUE)
bart_res
```
```{r}
summary(bart_res)
plot_sigma(bart_res)
plot_est(bart_res)
plot_indiv(bart_res)
```
```{r}
bart_res <- bartc(outcome_var, treatment_var, factor(S1) + factor(S2) + factor(S3) + factor(S3) + factor(S4) + factor(I1) + factor(I2) + factor(PARTY7) + factor(REL1) + factor(REL2) + PPAGE + factor(PPEDUCAT)+ factor(PPETHM) + factor(PPGENDER)  + factor(PPHHHEAD) + PPHHSIZE + factor(PPHOUSE) + factor(PPINCIMP) + factor(PPMARIT) + factor(PPMSACAT) + factor(PPREG4) + factor(PPRENT) + PPT01 + PPT25 + PPT612 + PPT1317 + PPT18OV + factor(PPWORK) + factor(PPNET), data = data5, method.rsp = "bart", method.trt = "bart", estimand = 'att', crossvalidate = TRUE, commonSup.rule = "sd", commonSup.cut = 1)
bart_res
summary(bart_res)
plot_sigma(bart_res)
plot_est(bart_res)
plot_indiv(bart_res)
plot_support(bart_res)
```

```{r}
bart_res <- bartc(outcome_var, treatment_var, factor(S1) + factor(S2) + factor(S3) + factor(S3) + factor(S4) + factor(I1) + factor(I2) + factor(PARTY7) + factor(REL1) + factor(REL2) + PPAGE + factor(PPEDUCAT)+ factor(PPETHM) + factor(PPGENDER)  + factor(PPHHHEAD) + PPHHSIZE + factor(PPHOUSE) + factor(PPINCIMP) + factor(PPMARIT) + factor(PPMSACAT) + factor(PPREG4) + factor(PPRENT) + PPT01 + PPT25 + PPT612 + PPT1317 + PPT18OV + factor(PPWORK) + factor(PPNET), data = data5, method.rsp = "bart", method.trt = "bart", estimand = 'att', crossvalidate = TRUE, commonSup.rule = "chisq", commonSup.cut = 0.05)
bart_res
summary(bart_res)
plot_sigma(bart_res)
plot_est(bart_res)
plot_indiv(bart_res)
plot_support(bart_res)
```

# Prop score + 1-1 matching with replacement

## Computing prop score and matching with replacement to restructure the dataset
```{r}
# matchitobject0 = MatchIt::matchit(treatment_var ~ S1_1 + S1_2 + S1_3 + S1_4 + S2_1 + S2_2 + S2_3 + S2_4 + + S3_1 + S3_2 + S3_3 + S3_4 + S4_1 + S4_2 + S4_3 + S4_4 + I1_1 + I1_2 + I1_3 + I1_4 + I2_1 + I2_2 + I2_3 + I2_4 + PARTY7_1 + PARTY7_2 + PARTY7_3 + PARTY7_4 + PARTY7_5 + PARTY7_6 + PARTY7_7 + REL1_1 + REL1_2 + REL1_3 + REL1_4 + REL1_5 + REL1_6 + REL1_8 + REL1_9 + REL1_10 + REL1_11 + REL1_12 + REL1_13 + REL2_1 + REL2_2 + REL2_3 + REL2_4 + REL2_5 + REL2_6 + PPAGE + PPEDUCAT_1 + PPEDUCAT_2 + PPEDUCAT_3 + PPEDUCAT_4 + PPETHM_1 + PPETHM_2 + PPETHM_4 + gender_cat + PPHHHEAD + PPHHSIZE + PPHOUSE_1 + PPHOUSE_2 + PPHOUSE_3 + PPHOUSE_4 + PPHOUSE_5 + PPINCIMP_1 + PPINCIMP_2 + PPINCIMP_3 + PPINCIMP_4 + PPINCIMP_5 + PPINCIMP_6 + PPINCIMP_7 + PPINCIMP_8 + PPINCIMP_9 + PPINCIMP_10 + PPINCIMP_11 + PPINCIMP_12 + PPINCIMP_13 + PPINCIMP_14 + PPINCIMP_15 + PPINCIMP_16 + PPINCIMP_17 + PPINCIMP_18 + PPINCIMP_19 + PPMARIT_1 + PPMARIT_2 + PPMARIT_3 +PPMARIT_4 + PPMARIT_5 + PPMARIT_6 + PPMSACAT + PPREG4_1 + PPREG4_2 + PPREG4_3 + PPREG4_4 + PPRENT_1 + PPRENT_2 + PPRENT_3 + PPT01 + PPT25 + PPT612 + PPT1317 + PPT18OV + PPWORK_1 +  PPWORK_2 + PPWORK_3 + PPWORK_4 + PPWORK_5 + PPWORK_6 + PPWORK_7 + PPNET, data5, distance = "glm", link = "probit", replace = TRUE, method = "nearest")
matchitobject0 = MatchIt::matchit(treatment_var ~ factor(S1) + factor(S2) + factor(S3) + factor(S3) + factor(S4) + factor(I1) + factor(I2) + factor(I1):factor(I2) + factor(PARTY7) + factor(REL1) + PPAGE + factor(PPEDUCAT)+ factor(PPETHM) + factor(PARTY7):factor(PPEDUCAT) + factor(PPGENDER) + factor(PPGENDER):factor(PPWORK) + factor(PPHHHEAD) + PPHHSIZE + factor(PPHOUSE) + factor(PPINCIMP) + factor(PPMARIT) + factor(PPMSACAT) + factor(PPREG4) + factor(PPRENT) + PPT01 + PPT25 + PPT612 + PPT1317 + PPT18OV + factor(PPWORK) + factor(PPNET) + factor(PPNET):factor(PPMSACAT), data5, distance = "glm", link = "probit", replace = TRUE, method = "nearest")
```


## Assessing balance and overlap

```{r}
matchitobject0_sum <- summary(matchitobject0, standardize=TRUE)
matchitobject0_sum 
plot(matchitobject0_sum, var.order = "matched") 
# plot(matchitobject0_sum_unstd, var.order = "matched") 
```

```{r}
matchitobject0_sum_unstd <- summary(matchitobject0, standardize=FALSE)
matchitobject0_sum_unstd
```

```{r}
plot(matchitobject0, type = 'histogram', interactive=FALSE)
```

## Density plots per confounder to assess balance
```{r}
# plot(matchitobject0, type = 'density', which.xs = c('S1_4'))
# plot(matchitobject0, type = 'density', which.xs = c('S2_1','S2_2','S2_3'))
# plot(matchitobject0, type = 'density', which.xs = c('S2_4'))
# plot(matchitobject0, type = 'density', which.xs = c('S3_1','S3_2','S3_3'))
# plot(matchitobject0, type = 'density', which.xs = c('S3_4'))
# plot(matchitobject0, type = 'density', which.xs = c('S4_1','S4_2','S4_3'))
# plot(matchitobject0, type = 'density', which.xs = c('S4_4'))
# plot(matchitobject0, type = 'density', which.xs = c('I1_1','I1_2','I1_3'))
# plot(matchitobject0, type = 'density', which.xs = c('I1_4'))
# plot(matchitobject0, type = 'density', which.xs = c('I2_1','I2_2','I2_3'))
# plot(matchitobject0, type = 'density', which.xs = c('I2_4'))
# plot(matchitobject0, type = 'density', which.xs = c('PARTY7_1','PARTY7_2','PARTY7_3'))
# plot(matchitobject0, type = 'density', which.xs = c('PARTY7_4','PARTY7_5','PARTY7_6'))
# plot(matchitobject0, type = 'density', which.xs = c('PARTY7_7'))
# plot(matchitobject0, type = 'density', which.xs = c('REL1_1','REL1_2','REL1_3'))
# plot(matchitobject0, type = 'density', which.xs = c('REL1_4','REL1_5','REL1_6'))
# plot(matchitobject0, type = 'density', which.xs = c('REL1_8','REL1_9','REL1_10'))
# plot(matchitobject0, type = 'density', which.xs = c('REL1_11','REL1_12','REL1_13'))
```

```{r}
# plot(matchitobject0, type = 'density', which.xs = c('REL2_1','REL2_2','REL2_3'))
# plot(matchitobject0, type = 'density', which.xs = c('REL2_4','REL2_5','REL2_6'))
```

```{r}
# plot(matchitobject0, type = 'density', which.xs = c('PPEDUCAT_1','PPEDUCAT_2','PPEDUCAT_3'))
# plot(matchitobject0, type = 'density', which.xs = c('PPEDUCAT_4','PPETHM_1','PPETHM_2'))
# plot(matchitobject0, type = 'density', which.xs = c('PPETHM_4','PPHOUSE_1','PPHOUSE_2'))
# plot(matchitobject0, type = 'density', which.xs = c('PPHOUSE_3','PPHOUSE_4','PPHOUSE_5'))
```

```{r}
# plot(matchitobject0, type = 'density', which.xs = c('PPAGE', 'gender_cat','PPHHHEAD'))
# plot(matchitobject0, type = 'density', which.xs = c('PPMSACAT', 'PPNET','PPHHSIZE'))
```

```{r}
# plot(matchitobject0, type = 'density', which.xs = c('PPINCIMP_1','PPINCIMP_2','PPINCIMP_3'))
# plot(matchitobject0, type = 'density', which.xs = c('PPINCIMP_4','PPINCIMP_5','PPINCIMP_6'))
# plot(matchitobject0, type = 'density', which.xs = c('PPINCIMP_7','PPINCIMP_8','PPINCIMP_9'))
# plot(matchitobject0, type = 'density', which.xs = c('PPINCIMP_10','PPINCIMP_11','PPINCIMP_12'))
# plot(matchitobject0, type = 'density', which.xs = c('PPINCIMP_13','PPINCIMP_14','PPINCIMP_15'))
# plot(matchitobject0, type = 'density', which.xs = c('PPINCIMP_16','PPINCIMP_17','PPINCIMP_18'))
# plot(matchitobject0, type = 'density', which.xs = c('PPINCIMP_19','PPMARIT_1','PPMARIT_2'))
# plot(matchitobject0, type = 'density', which.xs = c('PPMARIT_3','PPMARIT_4','PPMARIT_5'))
# plot(matchitobject0, type = 'density', which.xs = c('PPMARIT_6','PPREG4_1','PPREG4_2'))
# plot(matchitobject0, type = 'density', which.xs = c('PPREG4_3','PPREG4_4','PPRENT_1'))
# plot(matchitobject0, type = 'density', which.xs = c('PPRENT_2','PPRENT_3'))
# plot(matchitobject0, type = 'density', which.xs = c('PPWORK_1','PPWORK_2','PPWORK_3'))
# plot(matchitobject0, type = 'density', which.xs = c('PPWORK_4','PPWORK_5','PPWORK_6'))
# plot(matchitobject0, type = 'density', which.xs = c('PPWORK_7','PPT01','PPT25'))
# plot(matchitobject0, type = 'density', which.xs = c('PPT612','PPT1317','PPT18OV'))
```

## Treatment effect estimation on restructure dataset
```{r}
treatment_effect0 <- lm(outcome_var ~ treatment_var + factor(S1) + factor(S2) + factor(S3) + factor(S3) + factor(S4) + factor(I1) + factor(I2)+ factor(PARTY7) + factor(REL1) + PPAGE + factor(PPEDUCAT)+ factor(PPETHM) + factor(PPGENDER) + factor(PPHHHEAD) + PPHHSIZE + factor(PPHOUSE) + factor(PPINCIMP) + factor(PPMARIT) + factor(PPMSACAT) + factor(PPREG4) + factor(PPRENT) + PPT01 + PPT25 + PPT612 + PPT1317 + PPT18OV + factor(PPWORK) + factor(PPNET), data=data5, model=TRUE, x=TRUE, y=TRUE, qr=TRUE, weights=matchitobject0$weights)
summary(treatment_effect0)
```

# IPTW
```{r}
iptw_model = glm(treatment_var ~ factor(S1) + factor(S2) + factor(S3) + factor(S3) + factor(S4) + factor(I1) + factor(I2) + factor(I1):factor(I2) + factor(PARTY7) + factor(REL1) + PPAGE + factor(PPEDUCAT)+ factor(PPETHM) + factor(PARTY7):factor(PPEDUCAT) + factor(PPGENDER) + factor(PPGENDER):factor(PPWORK) + factor(PPHHHEAD) + PPHHSIZE + factor(PPHOUSE) + factor(PPINCIMP) + factor(PPMARIT) + factor(PPMSACAT) + factor(PPREG4) + factor(PPRENT) + PPT01 + PPT25 + PPT612 + PPT1317 + PPT18OV + factor(PPWORK) + factor(PPNET) + factor(PPNET):factor(PPMSACAT), data = data5, family = binomial(link ="logit"))
```

```{r}
iptw_data = augment_columns(iptw_model,data5,type.predict = "response")%>%rename(propensity= .fitted)
weights = ifelse(iptw_data$treatment_var == 1,1,iptw_data$propensity/(1-iptw_data$propensity))
m.iptw <- MatchIt::matchit(treatment_var ~ factor(S1) + factor(S2) + factor(S3) + factor(S3) + factor(S4) + factor(I1) + factor(I2) + factor(I1):factor(I2) + factor(PARTY7) + factor(REL1) + PPAGE + factor(PPEDUCAT)+ factor(PPETHM) + factor(PARTY7):factor(PPEDUCAT) + factor(PPGENDER) + factor(PPGENDER):factor(PPWORK) + factor(PPHHHEAD) + PPHHSIZE + factor(PPHOUSE) + factor(PPINCIMP) + factor(PPMARIT) + factor(PPMSACAT) + factor(PPREG4) + factor(PPRENT) + PPT01 + PPT25 + PPT612 + PPT1317 + PPT18OV + factor(PPWORK) + factor(PPNET) + factor(PPNET):factor(PPMSACAT), data = iptw_data, method = NULL, distance = "glm", link = "probit", s.weights=weights)
iptw_summ_obj <- summary(m.iptw, data=iptw_data) 
iptw_summ_obj_unstd <- summary(m.iptw, standardize=FALSE)


iptw_summ_obj
```




```{r}
iptw_summ_obj_unstd
plot(iptw_summ_obj, var.order = "unmatched")
plot(m.iptw, type = 'histogram', interactive=FALSE)
```
```{r}
linreg_treatment_effect <- lm(outcome_var ~ treatment_var + factor(S1) + factor(S2) + factor(S3) + factor(S4) + factor(I1) + factor(I2) + factor(PARTY7) + factor(REL1) + factor(REL2) + factor(PPEDUCAT) + factor(PPETHM) + factor(PPHOUSE) + factor(PPINCIMP) + I(PPAGE^2) +factor(PPGENDER) + factor(PPHHHEAD) + PPHHSIZE + factor(PPMARIT) + factor(PPREG4) + factor(PPMSACAT) + factor(PPRENT) + PPT01 + PPT25 + PPT612 + PPT1317 + PPT18OV + factor(PPWORK) + factor(PPNET) + factor(PPINCIMP):factor(PPEDUCAT) + factor(PPNET):factor(PPMSACAT) + factor(REL1):factor(REL2) + factor(REL1):factor(PARTY7) + factor(PPWORK):factor(PPGENDER) + factor(REL1):factor(PPETHM) + factor(PPGENDER):factor(PPINCIMP) + factor(PPINCIMP):factor(S1)  + factor(PARTY7):factor(PPREG4)  + factor(I1):factor(I2), data = iptw_data, weights= m.iptw$weights, model = TRUE, x = TRUE, y = TRUE, qr = TRUE)
summary(linreg_treatment_effect)
```



# Genetic Matching
```{r}
gen_matchitobject = MatchIt::matchit(treatment_var ~ factor(S1) + factor(S2) + factor(S3) + factor(S3) + factor(S4) + factor(I1) + factor(I2) + factor(I1):factor(I2) + factor(PARTY7) + factor(REL1) + PPAGE + factor(PPEDUCAT)+ factor(PPETHM) + factor(PARTY7):factor(PPEDUCAT) + factor(PPGENDER) + factor(PPGENDER):factor(PPWORK) + factor(PPHHHEAD) + PPHHSIZE + factor(PPHOUSE) + factor(PPINCIMP) + factor(PPMARIT) + factor(PPMSACAT) + factor(PPREG4) + factor(PPRENT) + PPT01 + PPT25 + PPT612 + PPT1317 + PPT18OV + factor(PPWORK) + factor(PPNET) + factor(PPNET):factor(PPMSACAT), data5, distance = "glm", link = "probit", replace = TRUE, method = "genetic")
gen_matchitobject_sum <- summary(gen_matchitobject)
summary(gen_matchitobject, standardize =  FALSE)
gen_matchitobject_sum
```

```{r}
# matchitobject1_sum <- summary(, standardize=TRUE)
# matchitobject1_sum
plot(gen_matchitobject_sum, var.order = "matched")
plot(gen_matchitobject, type = 'histogram', interactive=FALSE)
```

```{r}
treatment_effect_gen1 <- lm(outcome_var ~ treatment_var + factor(S1) + factor(S2) + factor(S3) + factor(S3) + factor(S4) + factor(I1) + factor(I2)+ factor(PARTY7) + factor(REL1) + PPAGE + factor(PPEDUCAT)+ factor(PPETHM) + factor(PPGENDER) + factor(PPHHHEAD) + PPHHSIZE + factor(PPHOUSE) + factor(PPINCIMP) + factor(PPMARIT) + factor(PPMSACAT) + factor(PPREG4) + factor(PPRENT) + PPT01 + PPT25 + PPT612 + PPT1317 + PPT18OV + factor(PPWORK) + factor(PPNET), data=data5, model=TRUE, x=TRUE, y=TRUE, qr=TRUE, weights=gen_matchitobject$weights)
summary(treatment_effect_gen1)
```

```{r}
genmatch = MatchIt::matchit(treatment_var ~ factor(S1) + factor(S2) + factor(S3) + factor(S4) + factor(I1) + factor(I2) + factor(PARTY7) + factor(REL1) + factor(REL2) + factor(PPEDUCAT) + factor(PPETHM) + factor(PPHOUSE) + factor(PPINCIMP) + I(PPAGE^2) +factor(PPGENDER) + factor(PPHHHEAD) + PPHHSIZE + factor(PPMARIT) + factor(PPREG4) + factor(PPMSACAT) + factor(PPRENT) + PPT01 + PPT25 + PPT612 + PPT1317 + PPT18OV + factor(PPWORK) + factor(PPNET) + factor(PPINCIMP):factor(PPEDUCAT) + factor(PPNET):factor(PPMSACAT) + factor(REL1):factor(REL2) + factor(REL1):factor(PARTY7) + factor(PPWORK):factor(PPGENDER) + factor(REL1):factor(PPETHM) + factor(PPGENDER):factor(PPINCIMP) + factor(PPINCIMP):factor(S1)  + factor(PARTY7):factor(PPREG4)  + factor(I1):factor(I2), data5, distance = "glm", link = "probit", replace = TRUE, method = "genetic")
genmatch <- summary(genmatch, standardize=TRUE)
genmatch_unstd <- summary(genmatch, standardize=FALSE)
genmatch 
genmatch_unstd
```


